Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-24 notes.tex
rewrote the notes with dimer+bath auxiliary model in mind

	\sum_{\vec k}^\text{eff. bath} = c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}

@@

	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff. bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{1\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}

@@

%\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers: tiling the lattice with Anderson molecules}
\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers}
We will follow the strategy outlined in the previous section. For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site. Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites. This is achieved by applying periodic boundary conditions on the edges of the lattice. A square 2d lattice is thus placed on a 2-torus.
For each nearest-neighbour pair \(i,j\), we will create a local Hamiltonian \(H^D_{i,j}\) from the Hamiltonian of the Hubbard dimer with bath (we will interpret the effective bath as the remaining \(N-2\) sites of the lattice, apart from \(i,j\)). We will need to suitably transform the Hamiltonian parameters \(U^D, t^D\), but we will figure those out as we go along. Since the number of nearest neighbour pairs is \(\frac{Nw}{2}\), the general Hubbard Hamiltonian should be the average of these local Hamiltonians. 
We recall the dimer+bath Hamiltonian here, since we are going to create the full Hamiltonian by combining various realizations of that Hamiltonian:

@@

	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff. bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}

@@

We will first create a "local" Hamiltonian, where one particular nearest neighbour pair \((i,j)\) makes up the dimer sites of the Hamiltonian, while the rest \(N-2\) sites of the lattice make up the effective bath. The zero-mode site of the effective bath is mapped to one of the nearest-neighbours of \(i\) or \(j\)
	\tilde H^D_(i,j) = H^D(i, j) - t^D \sum_{\vec k}^\text{eff. bath (i,j)}\left(c^\dagger_{i\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath (i,j)}\epsilon_{\vec k}\hat n_{\vec k}
\(H^D(0 \to i, 1 \to j)\) is the Hubbard dimer Hamiltonian in eq.~\ref{dimer_ham} with the indices 0 and 1 replaced by \(i, j\) respectively. Note that this local Hamiltonian actually has all the hoppings of the full Hubbard model, but the correlation is present just on the sites \(i,j\). We havent transformed the dimer parameters \(U^D, t^D\) to the Hubbard parameters yet.
If we now sum over all the nearest-neighbour pairs and take the average of all the Hamiltonians (\(\frac{1}{2}Nw\) in number), we get
	\tilde H &= \frac{2}{Nw}\sum_{\left<ij \right>}^N H^D_{i,j} \\
		 &= -t^A\sum_{\left<ij\right>}\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + \frac{2}{N}\sum_i U \tau_{i \uparrow}\tau_{i \downarrow}\\
		      &= \frac{1}{Nw}\left[\sum_{\sigma, i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N. of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right] \\
		      &= \frac{1}{Nw}\left[-t^D 2\sum_{\sigma, \left<ij\right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + 2 U^D\sum_{\left<ij\right>} \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + 2 U^D\sum_{\left<ij\right>} \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
		      &= \frac{2}{Nw}\sum_{\left<ij\right>}\left[-t^D \sum_\sigma \left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + U^D\left(\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right)\right]\\
		      &= \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
There we used the identity
	\sum_{i=1}^N\sum_{j \in \text{NN of }j} = 2\sum_{\left<ij\right>}
The sum $\left<ij\right>$ is over all nearest-neighbour pairs. Thus, $\tilde H$ can be written as

@@

	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma, \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)

@@

The conclusion is that on tiling the Hubbard dimer Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters" given by

@@

	\tilde t = \frac{2t^D}{Nw}~~,~~ \tilde U = \frac{2U^D}{N}~.

@@

The claim made in a previous section was that this Hamiltonian is very close to a similarity transformed Hubbard Hamiltonian:
	\tilde{H} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \equiv  \mathcal{U} H^H  \mathcal{U}^{-1}~,
where $\mathcal{U}$ is in general distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian. As shown earlier, $U$ transformation that involves three steps: the URG transformations $\mathcal{U}_A$, the extracting of the zero mode $Z$ and the tiling procedure outline in this section, $T$
	\mathcal{U} = T Z \mathcal{U}_{A}~.

@@

@@

	\mathcal{\tilde G}(\omega) = \frac{1}{\omega - \left(\tilde H - E_\text{GS}\right)}, && \mathcal{G}_D(\omega) = \frac{1}{\omega - \left(H^D - E_\text{GS}\right)}

@@

	\omega - \mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<\tilde i, \tilde j\right>}\left[\omega - \mathcal{G}_D^{-1}\left(\tilde i, \tilde j\right)\right]

@@

where $\mathcal{G}_D^{-1}(\tilde i,\tilde j)$ is the Greens function inverse matrix of the Hubbard dimer Hamiltonian with $\tilde i, \tilde j$ as the two sites. Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor. The factor is just the total number of nearest neighbour pairs, which is $\frac{Nw}{2}$. This allows it to cancel the $\omega$ on the LHS. The equation then simplifies to

@@

	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right)

@@

We will now calculate the site-diagonal and site-off-diagonal matrix elements for particle propagation. The site-diagonal matrix element is calculated between the state $\ket{\tilde i, \sigma} = \mathcal{U}c^\dagger_{i\sigma}\ket{\Phi_0}$ and its bra, while the off-diagonal one is between $\ket{\tilde j\sigma}$ and $\bra{\tilde i\sigma}$. Since it has already been shown that the matrix elements of the renormalised Hamiltonian are the same as those of the original Hamiltonian, we will directly replace the former with the latter. \\\\
First lets consider the diagonal matrix element at $\tilde i^\text{th}$ site. The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $\tilde i$ in one of the indices. There will be $w$ such terms, because $\tilde i$ has $w$ nearest neighbours. Thus, the right hand side will be a sum of $w$ terms, each term being the inverse Greens function of a Hubbard dimer. Each term will be a real space local Greens function, and because of translational invariance, it will be the same on both sites. %So we will represent the real space local inverse Greens function as $\left[\mathcal{G}_D^{-1}(\omega)\right]_{00}^{\sigma}$.
The entire thing is thus $w$ times this local Greens function.

@@

@@

	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}\times w = \frac{2}{N}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}

@@

We can expand the state $c^\dagger_{0\sigma}\ket{\tilde \Phi_0}$ and $c^\dagger_{1\sigma}\ket{\tilde \Phi_0}$ in terms of a complete set of orthogonal states:

@@

Due to the translation invariance, the coefficients $C^{0}_{n}$ and $C^{1}_{n}$ are independent of the site indices. The index $n$ actually defines a set of quantum numbers that characterize the state $\ket{n}$. For example it might be a combination of number of particles, parity and total spin angular momentum $(n \equiv n, P, S^z)$. One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other. The dimer will of course have 2 sites, which means the conduction bath will have $N-2$ sites, or $N-2$ momentum states. The set of eigenstates that have the total number of particles (combining the dimer and the bath) equal to $N+1$ will then form the basis in question. Since the dimer is decoupled from the bath, the total wavefunction will be a direct product of a Hubbard dimer wavefunction and a bath wavefunction.
	\ket{m,\alpha,\beta} = \Phi^D_{m,\alpha} \otimes \Psi^B_{N-m+1, \beta}
$\alpha$ is an internal quantum number of the Hubbard dimer while $\beta$ is that for the bath. The subscripts $m$ and $N-m+1$ label the total number of particles in each part of the wavefunction. These two labels have to add to $N+1$. Our choice of the $\ket{n}$ is motivated by noting that the effective auxiliary model we are invoking here is that of a Hubbard dimer connected to a bath via single-particle hybridisation; the eigenstates of the isolated dimer and bath subsystems then act as the natural choices of the orthogonal bases in which to expand the wavefunction for the single-particle excitation of the interacting system $c^\dagger_{0\sigma}\ket{\tilde \Phi_0}$. Further, while the eigenstates ($\Phi^D_{m,\alpha}$) of the Hubbard dimer are known analytically, we can safely assume the eigenstates of the bath ($\Psi^B_{N-m+1, \beta}$) to be a simple direct product of various single-particle Fock states in $k$-space. We then compute the matrix element of eq.\eqref{local_gf} for site $i$ and its immediate neighbours (i.e., a given realisation of a auxiliary model). Then, using translation invariance, we demand that this matrix element is independent of the site index $i$. The correctness of this auxiliary model approach hinges on how close the state $\ket{\tilde{\Phi_0}}$ is to the 2-site local nature of the exact ground state of the target model (here the Hubbard model on a given lattice). Further improvement can be made by improving (i) the state $\ket{\tilde{\Phi_0}}$ for the present auxiliary model (involving a Hubbard dimer), or (ii) choosing a better auxiliary model with an ``impurity" system that has more sites than two (i.e., a Bethe-Peierls improvement of the dimer auxiliary model).

@@

Since the Hubbard dimer of the ket $\ket{n}$ is an actual eigenstate, $\mathcal{G}_{D}^{-1}(\omega)$ will be diagonal in that basis:

@@

Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.We will extract this using the definition. This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$. This will not be a diagonal Greens function. Instead, it involves two nearest neighbour sites. %We call this Greens function $\left[\mathcal{G}_D^{-1}(\omega)\right]_{01}^\sigma$.

@@

	\left(\mathcal{G}_{H}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\sum_{n} |C^0_{n}|^2 \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\sum_{n} |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}

@@

	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {C^0_{n}}^* C^1_{n} \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}

@@

	G_H(\omega)_\text{loc} &= \left(\mathcal{G}_H(\omega)\right)_{ii} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ii}} = \frac{2}{N}\sum_n\left(|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}\right)\\
	G_H(\omega)_\text{nn} &= \left(\mathcal{G}_H(\omega)\right)_{ij} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ji}} = \frac{2}{Nw}\sum_n\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\\

@@

			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]

>>>>

	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}

@@

	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}

@@

%\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers: tiling the lattice with Anderson molecules}
\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers}
We will follow the strategy outlined in the previous section. For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site. Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites. This is achieved by applying periodic boundary conditions on the edges of the lattice. A square 2d lattice is thus placed on a 2-torus.
\\\\
For each nearest-neighbour pair \(i,j\), we will create a local Hamiltonian \(H^D_{i,j}\) from the Hamiltonian of the Hubbard dimer with bath (we will interpret the effective bath as the remaining \(N-2\) sites of the lattice, apart from \(i,j\)). We will need to suitably transform the Hamiltonian parameters \(U^D, t^D\), but we will figure those out as we go along. Since the number of nearest neighbour pairs is \(\frac{Nw}{2}\), the general Hubbard Hamiltonian should be the average of these local Hamiltonians. 
\\\\
We recall the dimer+bath Hamiltonian here, since we are going to create the full Hamiltonian by combining various realizations of that Hamiltonian:
\begin{equation}\begin{aligned}
	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff. bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
\end{aligned}\end{equation}
We now choose a particular nearest neighbour pair from the full lattice, say \((i,j\), and one site that is nearest neighbour to this pair, call that \(l\). We will first create a "local" Hamiltonian, where one particular nearest neighbour pair \((i,j)\) makes up the dimer sites of the Hamiltonian, while the rest \(N-2\) sites of the lattice make up the effective bath and the site \(l\) forms the zeroth site of the bath.
\begin{equation}\begin{aligned}
	\label{Hdjl}
	\tilde H^D(i, j, l) \equiv \tilde H^D(0\to i, 1\to j, z \to l) = H^D(i, j) - t^D \sum_{\sigma}\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^{\text{eff. bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\\
\end{aligned}\end{equation}
\(H^D(i, j)\) is the Hubbard dimer Hamiltonian in eq.~\ref{dimer_ham} with the indices 0 and 1 replaced by \(i, j\) respectively. This is not the total local Hamiltonian for the nearest neighbour pair \((i,j\), because it has just one nearest neighbour of the dimer, namely \(l\). To get the full thing, we need to \textit{average} over all the nearest neighbours of the pair \(i,j\), \(2(w-1)\) in number. What we mean by nearest neighbours of the dimer pair \((i,j)\) is made clear in \ref{dimer-nn}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.3\textwidth]{dimer-nn.png}
	\caption{Blue circles indicate the dimer sites (enclosed by dotted circle). Green circles are the sites that are nearest neighbour to the dimer and the ones that are being summed over under the index \(l\). Orange circles are sites that are \textit{not} nearest neighbour to the dimer.}
	\label{dimer-nn}
\end{figure}

The total  Hamiltonian for a particular dimer pair \((i,j)\) then looks like:

@@

	\tilde H^D(i, j) &= \frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}} \left[H^D(i, j) - t^D \sum_{\sigma}\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^{\text{eff. bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\right]\\
			 &= H^D(i, j) + \frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\left[- t^D \sum_\sigma\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k,\sigma}^{\text{eff. bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\right]

@@

We now translate this Hamiltonian over all nearest neighbour pairs on the lattice, and take the average:

@@

	\tilde H = \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D(i, j, l) = \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)

@@

% Note that this local Hamiltonian actually has all the hoppings of the full Hubbard model, but the correlation is present just on the sites \(i,j\). We havent transformed the dimer parameters \(U^D, t^D\) to the Hubbard parameters yet.
% \\\\
% If we now sum over all the nearest-neighbour pairs and take the average of all the Hamiltonians (\(\frac{1}{2}Nw\) in number), we get
% 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij \right>}^N H^D_{i,j} \\
% 		 &= -t^A\sum_{\left<ij\right>}\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + \frac{2}{N}\sum_i U \tau_{i \uparrow}\tau_{i \downarrow}\\
% 		 &= \frac{1}{Nw}\left[\sum_{\sigma, i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N. of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
% 		      &= \frac{1}{Nw}\left[-t^D 2\sum_{\sigma, \left<ij\right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + 2 U^D\sum_{\left<ij\right>} \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + 2 U^D\sum_{\left<ij\right>} \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
% 		      &= \frac{2}{Nw}\sum_{\left<ij\right>}\left[-t^D \sum_\sigma \left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + U^D\left(\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right)\right]\\
% 		      &= \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
% There we used the identity
% 	\sum_{i=1}^N\sum_{j \in \text{NN of }j} = 2\sum_{\left<ij\right>}
The sum $\left<ij\right>$ is over all nearest-neighbour pairs. 
% Thus, $\tilde H$ can be written as
% 	\label{H_tiled}
% 	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma, \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
The conclusion is that on tiling the Hubbard dimer+bath Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters" given by

@@

	\tilde t = \frac{2}{Nw}(1 + \frac{Nw}{2})t^D, &&\tilde U = \frac{2}{N}U^D

@@

% \\\\
% The claim made in a previous section was that this Hamiltonian is very close to a similarity transformed Hubbard Hamiltonian:
% 	\tilde{H} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \equiv  \mathcal{U} H^H  \mathcal{U}^{-1}~,
% where $\mathcal{U}$ is in general distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian. As shown earlier, $U$ transformation that involves three steps: the URG transformations $\mathcal{U}_A$, the extracting of the zero mode $Z$ and the tiling procedure outline in this section, $T$
% 	\mathcal{U} = T Z \mathcal{U}_{A}~.
\textcolor{red}{

@@

}

@@

	\mathcal{\tilde G}(\omega) = \frac{1}{\omega - \left(\tilde H - E_\text{GS}\right)}, && \mathcal{G}_D(\omega) = \frac{1}{\omega - \left(\tilde H^D(i,j,l) - E_\text{GS}\right)}

@@

	\omega - \mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<\tilde i, \tilde j\right>} \frac{1}{2(w-1)} \sum_{l \in \text{NN of j}}\left[\omega - \mathcal{G}_D^{-1}\left(\tilde i, \tilde j, \tilde l\right)\right]

@@

where $\mathcal{G}_D^{-1}(\tilde i,\tilde j, \tilde l)$ is the Greens function inverse matrix of the Hubbard dimer+bath Hamiltonian with $\tilde i, \tilde j$ as the two sites and \(\tilde l\) as the zero mode of the bath, eq.~\ref{Hdjl}, or equivalently, eq.~\ref{dimer_p_bat}. Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor. The factor is just the total number of nearest neighbour pairs, which is $\frac{Nw}{2}$. This allows it to cancel the $\omega$ on the LHS. The equation then simplifies to
	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of j}}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j, \tilde l\right)
Because of translational invariance, all values of \(l\) should give the same Greens function, and we can simplify this to

@@

	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\frac{1}{2(w-1)}\times 2(w-1)\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right) = \frac{2}{Nw}\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right)

@@

We dropped the index \(\tilde l\) on \(\mathcal{G}_D^{-1}\) to mean that any particular choice of \(\tilde l\) will do. We will now calculate the site-diagonal and site-off-diagonal matrix elements for particle propagation. The site-diagonal matrix element will be calculated between the state $\ket{\tilde i, \sigma} = \mathcal{U}c^\dagger_{i\sigma}\ket{\Phi_0}$ and its bra, while the off-diagonal one is between $\ket{\tilde j\sigma}$ and $\bra{\tilde i\sigma}$. Since it has already been shown that the matrix elements of the renormalised Hamiltonian are the same as those of the original Hamiltonian, we will directly replace the former with the latter. \\\\
First lets consider the diagonal matrix element at $\tilde i^\text{th}$ site. The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have the index $\tilde i$ on the dimer. There are $w$ terms that have the index \(\tilde i\) on the dimer corresponding to the $w$ nearest neighbours of \(\tilde i\). Thus, the right hand side will be a sum of $w$ terms, each term being the inverse Greens function of a Hubbard dimer+bath Hamiltonian. Each term will be a real space local Greens function, and because of translational invariance, it will be the same for all choices of the nearest neighbour of \(\tilde i\). %So we will represent the real space local inverse Greens function as $\left[\mathcal{G}_D^{-1}(\omega)\right]_{00}^{\sigma}$.

@@

	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\sum_{j \in \text{NN of i}}\bra{\tilde \Phi_0}c_{i\sigma}\mathcal{G}_{D}^{-1}(\omega, \tilde i, \tilde j)c^\dagger_{i\sigma}\ket{\tilde \Phi_0} = \frac{2}{N}\bra{\tilde \Phi_0}c_{i\sigma}\mathcal{G}_{D}^{-1}(\omega, \tilde i)c^\dagger_{i\sigma}\ket{\tilde \Phi_0}
Once we have stripped away the \(j,l\) dependence, we can view the RHS as simply the matrix element of the dimer-bath Hamiltonian eq.~\ref{dimer_p_bat} between the local states of the site zero of the bath:

@@

	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}

@@

Just to make it explicit, we repeat once more that \(\mathcal{G}_{D}^{-1}(\omega)\) is the inverse Greens function operator of the Hamiltonian in eq.~\ref{dimer_p_bat}.
We can expand the state $c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$ in terms of a complete set of orthogonal states:

@@

Due to the translation invariance, the coefficients $C^{0}_{n}$ and $C^{1}_{n}$ are independent of the site indices. The index $n$ actually defines a set of quantum numbers that characterize the state $\ket{n}$. For example it might be a combination of number of particles, parity and total spin angular momentum $(n \equiv n, P, S^z)$. In light of the Greens function we have in between te states, we choose the orthogonal set to be formed by the eigenstates of the dim
er+bath Hamiltonian.
% One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other. The dimer will of course have 2 sites, which means the conduction bath will have $N-2$ sites, or $N-2$ momentum states. The set of eigenstates that have the total number of particles (combining the dimer and the bath) equal to $N+1$ will then form the basis in question. Since the dimer is decoupled from the bath, the total wavefunction will be a direct product of a Hubbard dimer wavefunction and a bath wavefunction.
% 	\ket{m,\alpha,\beta} = \Phi^D_{m,\alpha} \otimes \Psi^B_{N-m+1, \beta}
% $\alpha$ is an internal quantum number of the Hubbard dimer while $\beta$ is that for the bath. The subscripts $m$ and $N-m+1$ label the total number of particles in each part of the wavefunction. These two labels have to add to $N+1$. Our choice of the $\ket{n}$ is motivated by noting that the effective auxiliary model we are invoking here is that of a Hubbard dimer connected to a bath via single-particle hybridisation; the eigenstates of the isolated dimer and bath subsystems then act as the natural choices of the orthogonal bases in which to expand the wavefunction for the single-particle excitation of the interacting system $c^\dagger_{0\sigma}\ket{\tilde \Phi_0}$. Further, while the eigenstates ($\Phi^D_{m,\alpha}$) of the Hubbard dimer are known analytically, we can safely assume the eigenstates of the bath ($\Psi^B_{N-m+1, \beta}$) to be a simple direct product of various single-particle Fock states in $k$-space. We then compute the matrix element of eq.\eqref{local_gf} for site $i$ and its immediate neighbours (i.e., a given realisation of a auxiliary model). Then, using translation invariance, we demand that this matrix element is independent of the site index $i$. The correctness of this auxiliary model approach hinges on how close the state $\ket{\tilde{\Phi_0}}$ is to the 2-site local nature of the exact ground state of the target model (here the Hubbard model on a given lattice). Further improvement can be made by improving (i) the state $\ket{\tilde{\Phi_0}}$ for the present auxiliary model (involving a Hubbard dimer), or (ii) choosing a better auxiliary model with an ``impurity" system that has more sites than two (i.e., a Bethe-Peierls improvement of the dimer auxiliary model).
% \\\\

@@

Since $\ket{n}$ is an actual eigenstate of the Hamiltonian that defines \(\mathcal{G}_{D}^{-1}(\omega)\), $\mathcal{G}_{D}^{-1}(\omega)$ will be diagonal in that basis:

@@

Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$. This will receive contribution from only that dimer+bath Hamiltonian that has \(i,j\) as the dimer sites. This will not be a real space diagonal Greens function. Instead, it involves two nearest neighbour sites. %We call this Greens function $\left[\mathcal{G}_D^{-1}(\omega)\right]_{01}^\sigma$.

@@

	\left(\mathcal{G}_{H}(\omega)\right)_{ii}^\sigma = \frac{4(w-1)}{N}\sum_{n} |C^0_{n}|^2 \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{4(w-1)}{N}\sum_{n} |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}

@@

	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{4(w-1)}{Nw}\sum_{n} {C^0_{n}}^* C^1_{n} \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{4(w-1)}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}

@@

	G_H(\omega)_\text{loc} &= \left(\mathcal{G}_H(\omega)\right)_{ii} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ii}} = \frac{4(w-1)}{N}\sum_n\left(|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}\right)\\
	G_H(\omega)_\text{nn} &= \left(\mathcal{G}_H(\omega)\right)_{ij} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ji}} = \frac{4(w-1)}{Nw}\sum_n\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\\

@@

			     &= \frac{4(w-1)}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
